DATA 621 - Business Analytics and Data Mining

### 2020-10-28 HW3/HW3_Final_AA.Rmd
Added prediction section.

A number of variables fell out of the model, such as `chas`, `dis`, and `zn`
amobg others. The remaining predictors are all significant, at least at the 10%
level, except for `rad.24`. However, from the last trace of the stepping routine
shown below, removing it would ***drastically*** reduce the models performance.
Lastly, while `rad.1` is the base case, `rad.2` and `rad.6` have disappeared as
well. This indicates that both `rad = 2` and `rad = 6` should be considered
indistinguishable from `rad = 1`. 
```
                    Df Deviance    AIC
<none>                   90.565 122.56
+ dis                1   89.191 123.19
+ zn                 1   89.558 123.56
+ tax                1   89.700 123.70
- ptratio            1   93.763 123.76
+ age                1   90.156 124.16
+ `nox:chasOnRiver`  1   90.224 124.22
- `rm:dis`           1   94.254 124.25
+ chas.OnRiver       1   90.273 124.27
+ rad.6              1   90.315 124.31
- lstat              1   94.364 124.36
+ `ptratio:medv`     1   90.494 124.49
+ rad.2              1   90.554 124.55
- rm                 1   95.001 125.00
- `indus:lstat`      1   95.633 125.63
- `indus:nox`        1   97.351 127.35
- indus              1   97.597 127.60
- medv               1   98.568 128.57
- rad.3              1  101.594 131.59
- rad.5              1  105.594 135.59
- rad.7              1  118.832 148.83
- nox                1  134.786 164.79
- rad.8              1  149.967 179.97
- rad.4              1  152.757 182.76
- rad.24             1  152.797 182.80
```

@@

compTable[2, 2] <- m2.metrics[1,3]
compTable[2, 3] <- 2 * m2_precise$.estimate * m2_recall$.estimate /
  (m2_precise$.estimate + m2_recall$.estimate)
compTable[2, 4] <- m2.metrics[2,3]
```

@@

@@

```{r appendix, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```
```{r loadData}
```
```{r sumstat}
```
```{r density}
```
```{r boxplot}
```
```{r correlation}
```
```{r model1_2_adjust}
```
```{r m12BC}
```
```{r m12applyBC}
```
```{r m12BC_plot}
```
```{r model1_coeff}
```
```{r m2setup}
```
```{r m2svm}
```
```{r m2stack}
```
```{r m2predict}
```
```{r m2Stats}
```
```{r m3trainTemp}
```
```{r m3Clust}
```
```{r m3dataPrep}
```
```{r m3Sum}
```
```{r comparison}
```
```{r model1_perf}
```
```{r m2TestSet}
```
```{r m3TestSet}
```
```{r selperfstat}
```

>>>>

A number of variables fell out of the model, such as `chas`, `dis`, and `zn`
among others. The remaining predictors are all significant, at least at the 10%
level, except for `rad.24`. However, from the last trace of the stepping routine
shown below, removing it would ***drastically*** reduce the models performance.
Lastly, while `rad.1` is the base case, `rad.2` and `rad.6` have disappeared as
well. This indicates that both `rad = 2` and `rad = 6` should be considered
indistinguishable from `rad = 1`. 
```
                    Df Deviance    AIC
<none>                   90.565 122.56
+ dis                1   89.191 123.19
+ zn                 1   89.558 123.56
+ tax                1   89.700 123.70
- ptratio            1   93.763 123.76
+ age                1   90.156 124.16
+ `nox:chasOnRiver`  1   90.224 124.22
- `rm:dis`           1   94.254 124.25
+ chas.OnRiver       1   90.273 124.27
+ rad.6              1   90.315 124.31
- lstat              1   94.364 124.36
+ `ptratio:medv`     1   90.494 124.49
+ rad.2              1   90.554 124.55
- rm                 1   95.001 125.00
- `indus:lstat`      1   95.633 125.63
- `indus:nox`        1   97.351 127.35
- indus              1   97.597 127.60
- medv               1   98.568 128.57
- rad.3              1  101.594 131.59
- rad.5              1  105.594 135.59
- rad.7              1  118.832 148.83
- nox                1  134.786 164.79
- rad.8              1  149.967 179.97
- rad.4              1  152.757 182.76
- rad.24             1  152.797 182.80
```

@@

compTable[2, 2] <- m2.metrics[1, 3]
compTable[2, 3] <- 2 * m2_precise$.estimate * m2_recall$.estimate /
  (m2_precise$.estimate + m2_recall$.estimate)
compTable[2, 4] <- m2.metrics[2, 3]
```

@@

All the models performed very well and classified the majority of the test set
properly. The difference between the three models was very slight. Only 7, 6, 
and 4 observations out of 92 were misclassified by the three models
respectively. Given the above statistics and confusion matrices, **Model 3**
barely edged out the other two and will be used to predict on the `eval` set.

## Predictions

```{r evalPred}
setDT(eval)
neval <- dim(eval)[[1]]
eval[, `:=`(chas = factor(chas, labels = c('OffRiver', 'OnRiver')),
          rad = factor(rad))]
evalVars <- dummyVars( ~ indus * nox + indus * lstat + chas * nox + 
                         ptratio * medv + rm * dis + .,
                       data = eval, fullRank = TRUE)
evaltstx <- predict(evalVars, newdata = eval)
evalPred <- predict(m3Fit, newdata = evaltstx)
evalPredP <- predict(m3Fit, newdata = evaltstx, type = 'prob')
predTable <- data.frame(TestID = seq_len(neval),
                        PredictedClass = ifelse(evalPred == "Below", 0, 1),
                        Prob_Is_0 = evalPredP$Below,
                        Prob_Is_1 = evalPredP$Above)
kable(predTable, digits = 3L, caption = "Predicted Classes and Probabilities")
```

@@

```{r appendix, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```
```{r loadData}
```
```{r sumstat}
```
```{r density}
```
```{r boxplot}
```
```{r correlation}
```
```{r model1_2_adjust}
```
```{r m12BC}
```
```{r m12applyBC}
```
```{r m12BC_plot}
```
```{r model1_coeff}
```
```{r m2setup}
```
```{r m2svm}
```
```{r m2stack}
```
```{r m2predict}
```
```{r m2Stats}
```
```{r m3trainTemp}
```
```{r m3Clust}
```
```{r m3dataPrep}
```
```{r m3Sum}
```
```{r comparison}
```
```{r model1_perf}
```
```{r m2TestSet}
```
```{r m3TestSet}
```
```{r selperfstat}
```
```{r evalPred}
```
